### 2020-10-20 thesis/chap_2.tex
adress comment 16
address comment 23

The workshop aimed to gather stakeholders from multiple groups:
\begin{enumerate}
  \item Representatives of Non-Governmental Organizations that are involved in the conservation of ecological connectivity within the study extent (i.e. Montérégie).
  \item Land use planners (“amenagistes”) of the administrative regions covered by the study extent (the 15 MRCs in Montérégie).
  \item Representatives of Ministries involved in conservation (MFFP, MELCC).
  \item Representatives of the UPA (“Union des producteurs agricoles”) in Montérégie.
  \item Representatives of the private forestry industry unions (“producteurs forestiers”)
\end{enumerate}
Of all the groups, only the last group was not represented. \\

@@

Perhaps the most important limitation of this work is the fact that the strong consensus which was quickly built during the workshop occurred in the absence of representatives from the forestry and farming industries which limits the representativity of consensus that was built. The participants present were mainly from NGOs, regional land use planning offices and ministries. This further illustrates the need for consensus mapping and the need for an iterative process with the goal to involve a larger diversity of stakeholders. Participatory research scholars have discussed the importance to consult and involve a diverse set of participants, representative of different knowledge systems, in efforts of participatory modelling \cite{gray_modeling_2012}.

>>>>

The workshop aimed to gather stakeholders from multiple groups:
\begin{enumerate}
  \item Representatives of Non-Governmental Organizations that are involved in the conservation of ecological connectivity within the study extent (i.e. Montérégie).
  \item Land use planners (“amenagistes”) of the administrative regions covered by the study extent (the 15 MRCs in Montérégie).
  \item Representatives of Ministries involved in conservation (MFFP, MELCC).
  \item Representatives of the UPA (“Union des producteurs agricoles”) in Montérégie.
  \item Representatives of the private forestry industry unions (“producteurs forestiers”)
\end{enumerate}
Although representants of this last group was invited to the activity, none attended the workshop. \\

@@

Perhaps the most important limitation of this work is the fact that the strong consensus which was quickly built during the workshop occurred with a low turnout from the farming industry, as well as in the absence of representatives from the forestry industry, which limits the representativity of consensus that was built. The participants present were mainly from NGOs, regional land use planning offices and ministries. This further illustrates the need for consensus mapping and the need for an iterative process with the goal to involve a larger diversity of stakeholders. Participatory research scholars have discussed the importance to consult and involve a diverse set of participants, representative of different knowledge systems, in efforts of participatory modelling \cite{gray_modeling_2012}.
